### 2025-07-08 factor-analysis.qmd
20250708 - tweaks

```{r}
#| label: fig-efaScreePlot1
#| fig-cap: "Scree Plot."
#| fig-alt: "Scree Plot."

@@

```{r}
#| label: fig-efaScreePlot2
#| fig-cap: "Scree Plot."
#| fig-alt: "Scree Plot."

@@

```{r}
#| label: fig-efaVSSPlot2
#| fig-cap: "Very Simple Structure Plot."
#| fig-alt: "Very Simple Structure Plot."

>>>>

```{r}
#| label: fig-efaScreePlot1
#| fig-cap: "Scree Plot: With Comparisons to Simulated and Resampled Data."
#| fig-alt: "Scree Plot: With Comparisons to Simulated and Resampled Data."

@@

```{r}
#| label: fig-efaScreePlot2
#| fig-cap: "Scree Plot with Parallel Analysis."
#| fig-alt: "Scree Plot with Parallel Analysis."

@@

```{r}
#| label: fig-efaVSSPlot2
#| fig-cap: "Model Indices by Number of Factors."
#| fig-alt: "Model Indices by Number of Factors."

### 2025-07-08 pca.qmd
20250708 - tweaks

```{r}
#| label: fig-pcaScreePlot1
#| fig-cap: "Scree Plot."
#| fig-alt: "Scree Plot."

@@

```{r}
#| label: fig-pcaScreePlot2
#| fig-cap: "Scree Plot."
#| fig-alt: "Scree Plot."

@@

We generated the very simple structure (VSS) plot in @fig-pcaVSSPlot using the `vss()` function of the `psych` package [@R-psych].

```{r}
#| label: fig-pcaVSSPlot
#| fig-cap: "Very Simple Structure Plot."
#| fig-alt: "Very Simple Structure Plot."

@@

>>>>

```{r}
#| label: fig-pcaScreePlot1
#| fig-cap: "Scree Plot: With Comparisons to Simulated and Resampled Data."
#| fig-alt: "Scree Plot: With Comparisons to Simulated and Resampled Data."

@@

```{r}
#| label: fig-pcaScreePlot2
#| fig-cap: "Scree Plot with Parallel Analysis."
#| fig-alt: "Scree Plot with Parallel Analysis."

@@

We generated the very simple structure (VSS) plots in Figures [-@fig-pcaVSSPlot1] and [-@fig-pcaVSSPlot2] using the `vss()` and `nfactors()` functions of the `psych` package [@R-psych].

```{r}
#| label: fig-pcaVSSPlot1
#| fig-cap: "Very Simple Structure Plot."
#| fig-alt: "Very Simple Structure Plot."

@@

```{r}
#| label: fig-pcaVSSPlot2
#| fig-cap: "Model Indices by Number of Components."
#| fig-alt: "Model Indices by Number of Components."

psych::nfactors(
  dataForPCA[pcaVars],
  rotate = "oblimin",
  fm = "pc")
```
